---
title: "ejer_graficos"
output: html_document
date: "2022-10-12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)

```


1)  Plot distance against stretch:
```{r}
ex1 <- data.frame(stretch=c(46,54,48,50,44,42,52), distance=c(148,182,173,166,109,141,166))

ex1
```
```{r}
ggplot(ex1, aes(x=stretch, y=distance)) + 
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks=seq(40, 60, 1)) +
  scale_y_continuous(breaks=seq(100, 200, 10))
```

2) The follwing data have ten observations taken during the years 1970-79, on October snow cover for Eurasia (snow cover is in millions of square kilometers).
```{r}
ex2 <- data.frame(year=c(1970:1979), snow.cover=c(6.5,12.0,14.9,10.0,10.7,7.9,21.9,12.5,14.5,9.2))
```

Plot snow.cover versus year.
```{r}
ggplot(ex2, aes(x=year, y=snow.cover)) + 
  geom_point() +
  geom_line() +
  scale_x_continuous(breaks=seq(1970, 1979, 1)) +
  scale_y_continuous(breaks=seq(0, 22, 5))
```
Plot a histogram of the snow.cover values.
```{r}
ggplot(ex2, aes(x=snow.cover)) +
  geom_histogram(bins = 4, binwidth = 5, fill="blue", color="black")
```
3) Given the following data:
```{r}

```





Create a function to convert ºF to ºC and in (inches) to mm.
```{r}

```

Plot Year vs. Warmest Minimum Temperature.
```{r}

```
Plot Year vs. Warmest Minimum Temperature and Coldest Minimum Temperature. Don’t forget to add a legend!
```{r}

```