---
title: "ejer_programming_structures"
output: html_document
date: "2022-10-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Programming Structures

1.Create an increasing function that indicates whether the elements of a given array are strictly increasing. Ordering the vector is not allowed.
```{r}
increasing<- function(arr){
  crece<- T
  final<- length(arr)-1 
  i<- 1 
  
  while (crece & i <= final) {
    if(arr[i] > arr[i+1]){
      crece<- F
    }
    i<- i+1
  }
  crece
}

caso1<- c(1:5)
caso2<- c(1,2,5,3)
increasing(caso1)
increasing(caso2)
```
2.Create a function "montecarlo" that calculates the estimation of the given integral. Check functions runif() and rnorm().
```{r}
montecarlo<- function(x){
#AYUDAAAAAAAAAAAAAAAAAA  
}
```

3.Create a list of five numeric arrays and order them after its creation.
```{r}
array1<- c(2,1,3)
array2<- c(5,1,2)
array3<- c(1,2,6,4)
array4<- c(7,1)
array5<- c(3,1,5)
my_list<- list(array1,array2,array3,array4,array5)

for(i in 1:length(my_list)){
  my_list[[i]]<- sort(my_list[[i]])
}
  my_list
```
Otra forma usando lapply
```{r}
my_list<- list(array1,array2,array3,array4,array5)
my_list<- lapply(my_list, sort)
my_list
```

4.Calculate the minimum value of each column of a matrix, but assume odd numbers are negative and even numbers are positive.
```{r}
negativeodd<- function(m){
  ifelse(m%%2 == 0, m, -m)
}

my_m<- matrix(c(1,2,3,4,5,7,8,4,22,5,11,22,33,44,53), ncol = 3, byrow = T)
my_m<- negativeodd(my_m)
my_m

#calculo los menores valores para cada col
min_col<- apply(my_m, 2, min)
min_col
```
5.Given a matrix return a list of all values greater than 7 of each row.
```{r}
mayor_7<- function(x){
  x[which(x>7)]
}

my_m<- matrix(c(1,2,3,4,5,7,8,4,22,5,11,22,33,44,53), ncol = 3, byrow = T)
greater_seven<- apply(my_m, 1, mayor_7)
greater_seven
```
