---
title: "ejer_functions"
output: html_document
date: "2022-10-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Functions

1.Create a function "impares" that given an array returns the number of odd elements it contains.
```{r}
impares <- function(array) {
    length(which(array%%2 != 0))
}

impares(1:5)
```
2.Create a function "cambio" that, given a matrix of integer numbers, returns a new matrix with all NA replaced by 0.
```{r}
cambio<- function(m) {
  m[which(is.na(m))] <-0
  m
}

m<- matrix(c(NA,3, 4,NA), nrow = 2, ncol = 2)
cambio(m)
```

3.Create a function "unir" that given two arrays returns a new array with the elements of both arrays without repetition (in the same order as in the original arrays).
```{r}
unir<- function(arr1, arr2) {
  union(arr1, arr2)
}

array1<- c(1,5,7,8)
array2<- c(7,8,2,9)
unir(array1, array2)
```

4.Create a function "vyc" that given a string returns a list of two components, one containing the vowels and the other the consonants (in alphabetical order and lowercase).
```{r}
vyc<- function(s){
  vowels<- c('a', 'e', 'i', 'o', 'u')
  
  s_split<- unlist(strsplit(s, ""))
  vocales<- s_split[s_split %in% vowels]
  consonantes<- s_split[!s_split %in% vowels]
  
  list(sort(vocales), sort(consonantes))
  
}

ejemplo<- "lechuga"
vyc(ejemplo)
```

5.Create a function "subpos" that given an array v and two values x and y (with y an optional parameter), returns a new array with the values included after the first x (if x is not there, start from the beggining) upto the first y after the first x (if y is not there, finish upto the end of the array). If y is not indicated, the function will return the values after the first x until the end of the array.

```{r}
subpos<- function(v, x, y=NA){
  ini_pos<- match(x, v, nomatch = 1)
  fin_pos<- match(y, v, nomatch = length(v))
  
  new_v<- v[ini_pos:fin_pos]
  new_v
}

subpos(1:4, 8, 3)
subpos(1:4, 2, 8)
subpos(1:4, 2)
```