---
title: "ejer_input_output"
output: html_document
date: "2022-10-07"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Input/Output

1.Ask the user to introduce with the keyboard a string s and a number n and show in the screen n times the string s (without spaces between words).
```{r}
s<- readline("Input string: ")
n<- readline("Input number: ")

out<- rep(s, n)
paste(out, collapse = '')
```

2.Create three files called dos.txt, tres.txt and cinco.txt containing the table of 2, 3 and 5 respectively (only include the first 10 values of each, one number in a separate line).
```{r}
multiplica<- 1:10

write.table(matrix(2 * multiplica, nrow = 10), "dos.txt", row.names=F, col.names=F)
write.table(matrix(3 * multiplica, nrow = 10), "tres.txt", row.names=F, col.names=F)
write.table(matrix(5 * multiplica, nrow = 10), "cinco.txt", row.names=F, col.names=F)
```

3.Load the three files created in the last exercise and create a matrix with three columns, one for each file content.
```{r}
tabla_dos<- scan("dos.txt")
tabla_tres<- scan("tres.txt")
tabla_cinco<- scan("cinco.txt")

m_tablas<- cbind(tabla_dos, tabla_tres, tabla_cinco)
m_tablas
```

4.Write the first five rows of the matrix created in the last exercise in a new file called prime.txt and the last five in another file called fin.txt. Both files must have the data separated by commas.
```{r}
write.table(m_tablas[1:5, ], "prime.txt", row.names = F, sep = ",") 
# write.table(head(m_tablas, 5), "prime.txt", row.names = F, sep = ",") 

write.table(m_tablas[6:10, ], "fin.txt", row.names = F, sep = ",") 
# write.table(tail(m_tablas, 5), "fin.txt", row.names = F, sep = ",") 
```

5.Given two numbers, f and c (given by the user using the keyboard), create a square figure of f rows and c collumns with character "x" (without spaces).
```{r}
f<- readline("Input rows: ")
c<- readline("Input columns: ")

rows<- paste(rep("x", c), collapse = '')
cat(paste(rep(rows, f), collapse = "\n"))
```
