---
title: "ejer_strings"
output: html_document
date: "2022-10-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Ejercicios Strings
# Homework (1st part)
1)  Create a string array contaning your first name and last names (e.g., ["Rocio", "Romero", Zaliz"]). Using that array and the R functions you just learned create a new string with the initial of your first name, a dot, and your last names (e.g., "R. Romero Zaliz").
```{r}
my_name<- c("Rafael", "Vazquez", "Conejo")
my_name

new_name<- paste(paste(substr(my_name[1],1,1), '.', sep = ""), my_name[2], my_name[3])
new_name
```

2)  Given an array of strings representing dates (e.g., [“2005-11-28”, “2015-10-18”, “2000-01-01”]), show only those corresponding to odd months (use format YEAR-MONTH-DAY).
```{r}
dates<- c("2005-11-28", "2015-10-18", "2000-01-01")
grep("[0-9]{4}-(0[1,3,5,7,9]|11)-[0-9]{2}", dates, value = T)

```

3)  Given a string with several words (e.g., “Esta es una frase, pero no cualquier frase.”) create an array with each of the words in the string (e.g., ["Esta","es","una","frase","pero","no","cualquier","frase"]). Take into account all possible punctuation characters.
```{r}
frase<- "Esta es una frase, pero no cualquier frase."
#necesito un separado cuando hay un signo de puntucación y un espacio y cuando acaba en signo de puntuacion
resultado<- unlist(strsplit(frase, split ="[[:blank:]]|[[:punct:]] |[[:punct:]]| "))
resultado
```

4)  Search in an array of strings those including only vocals "a" and/or "e" or none (check uppercase and lowercase).
```{r}
ejemplo<- c("avion", "gris", "gata", "TREN", "caer", "UNION")
ejemplo[-grep("(.*[i|u|o|I|U|O].*)", ejemplo)]
```

5)  Given three numeric arrays representing days, months and years, create an array with dates (only if they are valid) (Hint: research the as.Date function).
```{r}
days<- c("08", "21", "64", "12")
months<- c("02", "13", "10", "12")
years<- c("1999", "21", "2000", "1212")

dates<- as.Date(paste(years, months, days, sep = '-'), "%Y-%m-%d")
valid<- dates[!is.na(dates)]
valid
```


# Homework (2nd part)
Repeat homework (1st part) excersises using stringr functions
```{r}
library(tidyverse)
library(stringr)
```

1) Create a string array contaning your first name and last names (e.g., ["Rocio", "Romero", Zaliz"]). Using that array and the R functions you just learned create a new string with the initial of your first name, a dot, and your last names (e.g., "R. Romero Zaliz").
```{r}
my_name<- c("Rafael", "Vazquez", "Conejo")
my_name

new_name<- my_name[1] %>% str_sub(0,1) %>%
  str_c(".", collapse = "") %>%
  str_c(my_name[2], my_name[3], sep = " ")

new_name
```

2) Given an array of strings representing dates (e.g., [“2005-11-28”, “2015-10-18”, “2000-01-01”]), show only those corresponding to odd months (use format YEAR-MONTH-DAY).
```{r}
dates<- c("2005-11-28", "2015-10-18", "2000-01-01")
dates %>% str_subset("[0-9]{4}-(0[1,3,5,7,9]|11)-[0-9]{2}")
```

3)Given a string with several words (e.g., “Esta es una frase, pero no cualquier frase.”) create an array with each of the words in the string (e.g., ["Esta","es","una","frase","pero","no","cualquier","frase"]). Take into account all possible punctuation characters.
```{r}
frase<- "Esta es una frase, pero no cualquier frase."
#resultado<- unlist(strsplit(frase, split ="[[:punct:]] |[[:punct:]]| "))
resultado<- frase %>% str_split("[[:blank:]]|[[:punct:]] |[[:punct:]]| ")
resultado
```

4)Search in an array of strings those including only vocals "a" and/or "e" or none (check uppercase and lowercase).
```{r}
ejemplo<- c("avion", "gris", "gata", "TREN", "caer", "UNION")
ejemplo[str_detect(ejemplo, "(.*[i|u|o|I|U|O].*)", negate = T)]
```

5)Given three numeric arrays representing days, months and years, create an array with dates (only if they are valid) (Hint: research the as.Date function).
```{r}
days<- c("08", "21", "64", "12")
months<- c("02", "13", "10", "12")
years<- c("1999", "21", "2000", "1212")


dates<- as.Date(str_c(years, months, days, sep = '-'), "%Y-%m-%d")
valid<- dates[!is.na(dates)]
valid
```